----------------------------------
Title   : "PA1_template"
Author  : "Sridhar Somasundharam"
Date    : "Friday, December 12, 2014"
Output  : html_document
----------------------------------
Loading and preprocessing the data

1. Load the data (i.e. read.csv())
2. Process/transform the data (if necessary) into a format suitable for your analysis

```{r, echo=TRUE}
getwd()
setwd("C:/Users/ssomasundharam/Documents/Data Science/Coursera R/Reproducible Research")
```

What is mean total number of steps taken per day?

1. Make a histogram of the total number of steps taken each day
2. Calculate and report the mean and median total number of steps taken per day

```{r, echo=TRUE}

# acdata <- read.csv("activity.csv", na.strings=c("", "NA"))
# library(data.table)
# acdate <- data.table(acdata)
# acdate[, sum(complete.cases(acdata)), by = date]
# acstep <- acdate[,  by = date]
# acmean <- mean(acstep)
# head(acmean)
# achist <- hist(acdate$interval)
# achist

acdata <- read.csv("activity.csv")
library(data.table)
acdate <- data.table(acdata)
acstep <- acdate[,  by = steps]
achist <- hist(acdate$interval)

acmean <- c(acstep, mean, na.rm = TRUE)

atstep <- (acdata$steps)
atstep[is.na(atstep)] <- 0
median(atstep)
```

```{r, echo=TRUE}

# acmean
achist

```

Create a new dataset that is equal to the original dataset, but with the
missing data filled in original dataset is first three variables of the
activity dataframe

```{r, echo=TRUE}

sum(complete.cases(acdata))

# act <- plyr::ddply(acdata[1:3], .(interval), transform, steps = imp(steps), date = date, interval = interval)

```

Sort by date and interval

```{r, echo=TRUE}

# act <- act[order(act$date, act$interval),]

```

Renumber row names
```{r, echo=TRUE}

# row.names(act) <- 1:nrow(act)

```
