---
title: "PA1 Template"
author: "Sridhar Somasundharam"
date: "Wednesday, January 14, 2014"
output: html_document
---
Loading and preprocessing the data

1. Load the data (i.e. read.csv())
2. Process/transform the data (if necessary) into a format suitable for your analysis

```{r, echo=FALSE}
getwd()
setwd("C:/Users/ssomasundharam/Documents/Data Science/Coursera R/Reproducible Research")
```

What is mean total number of steps taken per day?

1. Make a histogram of the total number of steps taken each day
2. Calculate and report the mean and median total number of steps taken per day

```{r, echo=FALSE}

acdata <- read.csv("activity.csv")
acompe <- acdata[complete.cases(acdata),]
library(data.table)
acdate <- data.table(acompe)
acstep <- acdate[,sum(steps), by="date"]
library(ggplot2)
ggplot(acstep, aes(x = V1)) + geom_histogram() + xlab("Steps Taken Per Day")

```

# Mean and Median value for Total steps

```{r, echo=FALSE}
mean(acstep$V1)
median(acstep$V1)

```

What is the average daily activity pattern?

    Make a time series plot (i.e. type = "l") of the 5-minute interval (x-axis) and the average number of steps taken, averaged across all days (y-axis)

    Which 5-minute interval, on average across all the days in the dataset, contains the maximum number of steps?

# Average Number of Steps Taken
```{r, echo=FALSE}

acmean <- acdate[,mean(steps), by="interval"]
ggplot(acmean, aes(x = interval, y = V1)) + geom_line() + ylab("Average Steps")

```

# Maximum Average Steps

```{r, echo=FALSE}

acmean[which(acmean$V1 == max(acmean$V1)),]
sum(is.na(acmean$steps))

```

```{r, echo=FALSE}

acsteps <- acdata$steps
acsteps <- as.numeric(acsteps)
library(data.table)
acdate <- data.table(acmean)
for (i in 1:length(acsteps)) {
     if(is.na(acsteps[i]))
     acsteps[i] <- acmean[acmean$interval == acdata[i,3] ,2]
  }
acdata$steps <- acsteps


```


```{r, echo=FALSE}

acdate <- data.table(acdata)
a_step <- acdate[,sum(steps), by = "date"]
library(ggplot2)
ggplot(a_step, aes(x = V1)) + geom_histogram() + xlab("Steps Taken Per Day")

```

Mean and Median value

```{r, echo=FALSE}

mean(a_step$V1)
median(a_step$V1)

```

Renumber row names
```{r, echo=FALSE}

acdate$date <- as.Date(acdate$date)
acdate$day  <- weekdays(acdate$date)
acdate$weekend <- ifelse(acdate$day == "Saturday" | acdate$day == "Sunday", "Weekend", "Weekday")
acweek <- acdate[, mean(steps), by = c("interval", "weekend")]
ggplot(acweek, aes(x = interval, y = V1)) + facet_wrap(~weekend, nrow = 2) + geom_line() + ylab("Number of Steps")

```
