----------------------------------
Title   : "PA1_template"
Author  : "Sridhar Somasundharam"
Date    : "Friday, December 12, 2014"
Output  : "HTML Document"
----------------------------------
Loading and preprocessing the data

1. Load the data (i.e. read.csv())
2. Process/transform the data (if necessary) into a format suitable for your analysis

```{r, echo=TRUE}
getwd()
setwd("C:/Users/ssomasundharam/Documents/Data Science/Coursera R/Reproducible Research")
```

What is mean total number of steps taken per day?

1. Make a histogram of the total number of steps taken each day
2. Calculate and report the mean and median total number of steps taken per day

```{r, echo=TRUE}

acdata <- read.csv("activity.csv")
library(data.table)
acdate <- data.table(acdata)
acstep <- acdate[,  by = steps]
achist <- hist(acdate$interval)

acmean <- c(acstep, mean, na.rm = TRUE)

atstep <- (acdata$steps)
atstep[is.na(atstep)] <- 0
median(atstep)
```

```{r, echo=TRUE}

achist

```

What is the average daily activity pattern?

    Make a time series plot (i.e. type = "l") of the 5-minute interval (x-axis) and the average number of steps taken, averaged across all days (y-axis)

    Which 5-minute interval, on average across all the days in the dataset, contains the maximum number of steps?

```{r, echo=TRUE}

acdata <- read.csv("activity.csv")
day <- weekdays(as.Date(acdata$date))
wday <- as.POSIXlt(acdata$date)$wday
wd <- subset(acdata, wday != "0" | wday != "6")
plot(interval ~ date, wd, type = "l", main = "Average Number of Steps Taken")

```

Sort by date and interval

```{r, echo=TRUE}

plot(steps ~ interval, wd, type = "l", main = "Average Number of Steps Taken")

```

Renumber row names
```{r, echo=TRUE}

plot.ts(wd, ylab = "Interval", main = "Average Number of Steps Taken")

```
